### 2019-01-18 micro3_2.tex
Micro

As in previous exercise:
\begin{align*}
\frac{c_1(w)}{c_2(w)} = \frac{p_1}{p_2}\\ \frac{6}{2^{\frac{2}{3}}}\left(\frac{w_1}{w_2}\right)^{1/6} = \frac{6}{2^{\frac{2}{3}}3}\\
w_2 = 3^6w_1
\end{align*}
Now let us find the demand for factors:
\begin{align*}
a_1(w) = \begin{pmatrix}
\frac{\partial c_1(w)}{\partial w_1}\\
\frac{\partial c_1(w)}{\partial w_2}
\end{pmatrix} = \begin{pmatrix}
\left(\frac{2w_2}{w_1}\right)^{1/3}\\
\left(\frac{w_1}{2w_2}\right)^{2/3}
\end{pmatrix} = \begin{pmatrix}
2^{\frac{1}{3}}9\\
\frac{1}{2^{\frac{2}{3}}81}
\end{pmatrix}\\
a_2(w) = \begin{pmatrix}
\frac{\partial c_2(w)}{\partial w_1}\\
\frac{\partial c_2(w)}{\partial w_2}
\end{pmatrix} = \begin{pmatrix}
\left(\frac{w_2}{w_1}\right)^{1/2}\\
\left(\frac{w_1}{w_2}\right)^{1/2}
\end{pmatrix} = \begin{pmatrix}
27\\
\\
\frac{1}{27}
\end{pmatrix}\\
\frac{a_{11}}{a_{21}} = 2\cdot 3^6 > \frac{a_{12}}{a_{22}} = 3^6 > \frac{\bar{z_1}}{\bar{z_2}} = 2
\end{align*}
That means that in the equilibrium firm 1 should shut down.

\section*{Problem 3}
Suppose that for $w = (w_1, w_2) >> 0$, \begin{align*}
a_{11} = \frac{2}{3w_1}\left(\frac{w_1}{2/3}\right)^{2/3}\left(\frac{w_2}{1/3}\right)^{1/3}\\
a_{21} = \frac{1}{3w_2}\left(\frac{w_1}{2/3}\right)^{2/3}\left(\frac{w_2}{1/3}\right)^{1/3}\\
a_{12} = \frac{1}{3w_1}\left(\frac{w_1}{1/3}\right)^{1/3}\left(\frac{w_2}{2/3}\right)^{2/3}\\
a_{22} = \frac{2}{3w_2}\left(\frac{w_1}{1/3}\right)^{1/3}\left(\frac{w_2}{2/3}\right)^{2/3}\\
\end{align*}
where $a_j(w) := (a_{1j}(w); a_{2j}(w))$ is the conditional factor demand of firm $j$ that corresponds
to one unit of output. Assume $p_1 = p_2 = \frac{1}{2}$. Find the equilibrium factor allocation and
prices as a function of factor endowments $\bar{z_1}; \bar{z_2} > 0$. (Be sure to cover boundary equilibria,
if any.)

>>>>

As in previous exercise:
\begin{align*}
\frac{c_1(w)}{c_2(w)} = \frac{p_1}{p_2}\\ \frac{3}{2^{\frac{2}{3}}2}\left(\frac{w_1}{w_2}\right)^{1/6} = \frac{6}{2^{\frac{2}{3}}3}\\
w_1 = \frac{4^6}{3^6}w_2
\end{align*}
Now let us find the demand for factors:
\begin{align*}
a_1(w) = \begin{pmatrix}
\frac{\partial c_1(w)}{\partial w_1}\\
\frac{\partial c_1(w)}{\partial w_2}
\end{pmatrix} = \begin{pmatrix}
\left(\frac{2w_2}{w_1}\right)^{1/3}\\
\left(\frac{w_1}{2w_2}\right)^{2/3}
\end{pmatrix} = \begin{pmatrix}
2^{\frac{1}{3}}\frac{9}{16}\\
\\
\frac{256}{2^{\frac{2}{3}}81}
\end{pmatrix}\\
a_2(w) = \begin{pmatrix}
\frac{\partial c_2(w)}{\partial w_1}\\
\frac{\partial c_2(w)}{\partial w_2}
\end{pmatrix} = \begin{pmatrix}
\left(\frac{w_2}{w_1}\right)^{1/2}\\
\left(\frac{w_1}{w_2}\right)^{1/2}
\end{pmatrix} = \begin{pmatrix}
\frac{27}{64}\\
\\
\frac{64}{27}
\end{pmatrix}\\
\frac{\bar{z_1}}{\bar{z_2}}  = 2 > \frac{a_{11}}{a_{21}} = 2\cdot \frac{3^6}{4^6} > \frac{a_{12}}{a_{22}} = \frac{3^6}{4^6}
\end{align*}
That means that in the equilibrium firm 2 should indeed shut down. Thus, 
\begin{align*}
\begin{cases}
c_1(w) = p_1\\
\frac{a_{11}}{a_{21}} = \frac{\bar{z_1}}{\bar{z_2}}
\end{cases}\ \to 2\frac{w_2}{w_1} = 2 \to w_1 = w_2 \to \frac{3w_1}{2^{2/3}} = \frac{6}{2^{2/3}} \to w_1 = 2 = w_2
\end{align*}
Allocation:
\begin{align*}
\begin{pmatrix}
2\\
1
\end{pmatrix}, \begin{pmatrix}
0\\
0
\end{pmatrix}
\end{align*}
If $w_1 = w_2 = 2$ then $c_2(2, 2) = 4$ that is to produce one unit firm 2 should spend 4 dollars, while the price of unit of its production is only 3, that is it is indeed optimal for the second firm not to produce. Firm's 1 decision is also optimal because with $w_1 = w_2 = 2$ its cost of producing 1 unit becomes equal to price of the output. 
\section*{Problem 3}
Suppose that for $w = (w_1, w_2) >> 0$, \begin{align*}
a_{11} = \frac{2}{3w_1}\left(\frac{w_1}{2/3}\right)^{2/3}\left(\frac{w_2}{1/3}\right)^{1/3}\\
a_{21} = \frac{1}{3w_2}\left(\frac{w_1}{2/3}\right)^{2/3}\left(\frac{w_2}{1/3}\right)^{1/3}\\
a_{12} = \frac{1}{3w_1}\left(\frac{w_1}{1/3}\right)^{1/3}\left(\frac{w_2}{2/3}\right)^{2/3}\\
a_{22} = \frac{2}{3w_2}\left(\frac{w_1}{1/3}\right)^{1/3}\left(\frac{w_2}{2/3}\right)^{2/3}\\
\end{align*}
where $a_j(w) := (a_{1j}(w); a_{2j}(w))$ is the conditional factor demand of firm $j$ that corresponds
to one unit of output. Assume $p_1 = p_2 = \frac{1}{2}$. Find the equilibrium factor allocation and
prices as a function of factor endowments $\bar{z_1}; \bar{z_2} > 0$. (Be sure to cover boundary equilibria,
if any.)
